---
title: "Mini Project 2"
output: pdf_document
---

```{r, include=F, warning=F, echo=F}
library(tidyverse)
library(rio)
library(Stat2Data)
library(lsmeans)
library(asbio)
library(car)
```


```{r}
food <- import("review_cleaned2.csv") %>%
  drop_na("response")
```

## conditions check

```{r}
ggplot(food, aes(y=response, x=interaction(review, price)))+geom_boxplot()
```

```{r}
leveneTest(response ~ interaction(review,price), food)
```

No transformation needed. Doesn't violate equal variance rules.

```{r}
ggplot(food, aes(x=response, color=interaction(review,price)))+geom_density()

```

Some of the distributions not normal. Violation of normal distribution that might affect the accuracy of ANOVA analysis.

## ANOVA
Tukey check additive; it's additive as the slope is almost 0. so we don't need to include interaction of review and pricing in anova.

```{r}
TukeyNonaddPlot(response~price*review, data=food)
```

```{r}
aov_food <- aov(response~price+review, data=food)
summary(aov_food)
```

```{r}
plot(aov_food, which = 1)
plot(aov_food, which = 2)
```

## linear regression to check covariates

```{r}
lm <- lm(response~review+likely, data=food)
summary(lm)
```

## Post-hoc analysis

### Tukey HSD

```{r}
food$review <- as.factor(food$review)
food$price <- as.factor(food$price)
aov_food <- aov(response~price+review, data=food)
pairwise <- TukeyHSD(aov_food)
pairwise
plot(pairwise)
```

### Bonferroni

```{r}
bonfCI(food$response, interaction(food$review, food$price), conf.level = 0.95)
```

### Fisher's LSD

```{r}
pairw.anova(food$response, interaction(food$review,food$price ), method = "lsd", conf.level = 0.95)
```

## Effect size

```{r}
summary(aov_food)
```

```{r}
mse <- 2.72
SD <- sqrt(mse)
```

```{r}
twobad_mean <- mean(food$response[food$review=="2b"])
onegoneb_mean <- mean(food$response[food$review=="bg"])
twogood_mean <- mean(food$response[food$review=="2g"])
```

```{r}
effect_size1 <- abs(twobad_mean - twogood_mean)/SD
effect_size1
```

```{r}
effect_size2 <- abs(twobad_mean - onegoneb_mean)/SD
effect_size2
```

## Non-parametric test

```{r}
kruskal.test(response~interaction(review,price), data=food)

```

```{r}
kruskal.test(response~review, data=food)

```

```{r}
kruskal.test(response~price, data=food)

```




